Manuscript

### 2018-10-25 manuscript.Rmd

@@

GDSC:
```{r, eval=FALSE}
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC")
saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
```

>>>>

```{r}
ccle_data_allgenes <- readRDS("./data_munging/rds/ccle_data_18Q3_allgenes.rds")
ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]

knitr::kable(ccle_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

GDSC:
```{r, eval=FALSE}
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
system.time({ gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC") })
saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
```

```{r}
gdsc_data_allgenes <- readRDS("./data_munging/rds/gdsc_data_18Q3_allgenes.rds")
gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]

knitr::kable(gdsc_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```
